Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)

### 2020-06-02 doc/paper.tex
update docs

{\color{blue}We can also study on how much a neutrino mass model  or a sum rule can be excluded, assuming different true values for oscillation parameters.}
In this example, we present testing {\color{blue}atmospherical sum rule TM1~[cite]} in various true values of $\theta_{23}$ and $\delta$. We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results. Two parameters $x$ and $\eta$ are fixed at the best fit. In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code. 
%
We present this result in the left panel of Fig.~\ref{fig:th23_delta}. We further show the generality of \textbf{FaSE-GLoBES} by demonstrating the similar result for another model -- WFS in Eq.~(\ref{eq:WFS}) for DUNE and MOMENT, in right panel of Fig.~\ref{fig:th23_delta}. In this result, two mass-squared differences are fixed at the true values. 
%
%{\color{blue}And, true values of the other oscillation parameters are fixed at the best fit of NuFit4.0, and this setup is different from the left panel, in which we fix the other oscillation parameters at the model prediction for the true value.}
%
%As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the {\color{blue}assumed} true theory {\color{blue}($\vec{\theta}^{true}_{OSC}$)} and the hypothesis {\color{blue}($\vec{\theta}^{hyp}_{Model}$)}, \texttt{dof}. 
%{\color{blue}`The assumed true theory' here means that the oscillation parameters assumed for predicting the true event spectrum.} \textcolor{red}{[JT: what is the meaning of the true theory?]} 
%Here the number \texttt{dof} is $2$. 
%And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}. \textcolor{red}{[I don't understand this sentence.]} 
More details are presented in the user manual. 
%The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.

>>>>

{\color{blue}We can also study on how much a neutrino mass model  or a sum rule can be excluded, assuming different true values for oscillation parameters.}
In this example, we present testing {\color{blue}atmospherical sum rule TM1~[cite] and a supersymmetric flavour model $\Gamma_3$~[cite]} in various true values of $\theta_{23}$ and $\delta$. We compute the minimal $\chi^2$ value for the model with $r$ and $m_a$, varied with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results. Two parameters $x$ and $\eta$ are fixed at the best fit. In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code. 
%
We present this result in the left panel of Fig.~\ref{fig:th23_delta}. We further show the generality of \textbf{FaSE-GLoBES} by demonstrating the similar result for another model -- WFS in Eq.~(\ref{eq:WFS}) for DUNE and MOMENT, in right panel of Fig.~\ref{fig:th23_delta}. In this result, two mass-squared differences are fixed at the true values. 
%
%{\color{blue}And, true values of the other oscillation parameters are fixed at the best fit of NuFit4.0, and this setup is different from the left panel, in which we fix the other oscillation parameters at the model prediction for the true value.}
%
%As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the {\color{blue}assumed} true theory {\color{blue}($\vec{\theta}^{true}_{OSC}$)} and the hypothesis {\color{blue}($\vec{\theta}^{hyp}_{Model}$)}, \texttt{dof}. 
%{\color{blue}`The assumed true theory' here means that the oscillation parameters assumed for predicting the true event spectrum.} \textcolor{red}{[JT: what is the meaning of the true theory?]} 
%Here the number \texttt{dof} is $2$. 
%And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}. \textcolor{red}{[I don't understand this sentence.]} 
More details are presented in the user manual. 
%The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
